---
title: Simple Data Vizualization
author: Elizabeth Bross
date: '2017-09-24'
slug: scatter-plots-with-ggplot-and-ggiraph
categories: ["R"]
tags: ["R Markdown", "plot"]
---
##Scatter Plots with ggplot2 and ggiraph

Simple data vizualizations can provide insight that is easy to view and understand. To explore scatter plots, we will use MLB data from R's Lahman package. We will also use the ggiraph package to make an interactive scatter plot.

To begin this project, install all required R packages:

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

###Creating the dataset

In this example we will look at career homeruns vs. strikeouts for players with greater than 400 career homeruns. In order to do so, we much isolate the desired data from the Lahman package using dplyr. 

First, we will create a data frame containing career homeruns and career strikeouts.

```{r message=FALSE,warning=FALSE}
df<-Batting%>%
  group_by(playerID)%>%
  summarize(career_HR=sum(HR),career_SO=sum(SO))%>%
  filter(career_HR>=400)
```

Next, use dplyr's inner_join() function to add the nameFirst and nameLast variables to the initial data frame.

```{r message=FALSE,warning=FALSE}
HR_vs_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,career_HR,career_SO)
```

Finally, add a new column title "name" to the new HR_vs_SO data frame that includes both nameFirst and nameLast.

```{r message=FALSE,warning=TRUE}
HR_vs_SO$name<-paste(HR_vs_SO$nameFirst,HR_vs_SO$nameLast)

HR_vs_SO
```

###Creating the Scatter Plot

To begin your scatter plot, use the ggplot2 package to plot the points. Be sure to set the aes (the aesthetics) to the proper data. Career strikeouts should be on the x axis and career homeruns should be on the y axis. Use ggtitle and xlab and ylab to add a title and axis lables.

```{r message=FALSE,warning=FALSE}
g<-ggplot()+
  geom_point(data=HR_vs_SO,aes(x=career_SO,y=career_HR))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("career Homeruns")

```

Integrate the ggiraph package with the following additions to your initial graph. The tooltip will make your graph interactive.

```{r message=FALSE,warning=FALSE}
g<-ggplot()+
  geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=name,data_id=nameLast))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("career Homeruns")
```

Your graph will not be displayed until you use the ggiraph() function to render the plot. Use this line to view your results. Editing the hover_css will make your results easier to see.

```{r message=FALSE,warning=FALSE}
ggiraph(code=print(g),hover_css="fill:white;stroke:black")
```

